### 2017-10-18 Draft2/FieldsProperties.tex
Wording
Add constructor code

In subsequent sections, I will implement algorithms for both dynamic and growth arrays. In this section, I define the \textbf{fields} and \textbf{properties} these data structures are assumed to have for those algorithms. \textbf{Fields} are variables associated with an object that may be read from or written to. \textbf{Properties} are trivial, constant-time methods that do not change state.

@@

@@

>>>>

In subsequent sections, I will implement algorithms for both dynamic and growth arrays. In this section, I define fields and properties for these data structures which the algorithms will use. \textbf{Fields} are variables associated with an object that may be read from or written to. \textbf{Properties} are trivial, constant-time methods that do not change state.

@@

When a dynamic array is instantiated, the following code should run:

\begin{algorithm}
	\begin{algorithmic}
		\State $\listname.\FieldBuffer \gets \FuncNewArray(0)$
		\State $\listname.\FieldSize \gets 0$
	\end{algorithmic}
\end{algorithm}

@@

When a growth array is instantiated, the following code should run:

\begin{algorithm}
	\begin{algorithmic}
		\State $\listname.\FieldHead \gets \FuncNewArray(0)$
		\State $\listname.\FieldTail \gets \FuncNewDynamicArray()$
		\State $\listname.\FieldSize \gets 0$
		\State $\listname.\FieldCapacity \gets 0$
	\end{algorithmic}
\end{algorithm}
